\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-07 main.tex
First attempt at prev work

\title{\LARGE \bf
A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself %make better
}

@@

>>>>

\title{\LARGE \bf
Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
}

@@

Teachable computer-based agents have previously been used to encourage the ``protégé effect'',
wherein students invest more effort into learning when it is for a teachable agent 
than for themselves \cite{Chase2009}. Furthermore, robotic learning agents which 
employ the learning by teaching paradigm have been developed in settings such as 
vocabulary learning to take advantage of the engagement benefits in education. 
This differs from the established work which has focused exclusively on
on a robot learning physical skills for the benefit of the robot -- to play table 
tennis, for example -- not the human teacher. Indeed, as the handwriting that
the proposed robotic partner engages in is simulated and only for interaction 
purposes, it does not have not depend on capabilities to improve its writing.

We present the first known teachable agent which is capable
of artificially making mistakes typical of children learning handwriting, and
correcting them with external feedback. Such a system therefore exhibits the potential
to engage children in the learning by teaching paradigm in the context of
handwriting. Furthermore our work is concerned with learning of a physical skill, 
and so a robot has been used as the teachable agent to exploit its embodied nature.

Consequently, the learning agent developed has been embodied in a commercially
affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
leveraging synchronisation with a tablet display to simulate fine motor skills
otherwise infeasible for the robot. 
This use of a humanoid robot capable of physically demonstrating handwriting 
trajectories to its child learning partner is supported in this context by the potential 
for motor mimicry to yield significant improvements in handwriting interventions 
in which letter formations are demonstrated to participants \cite{Berninger1997}.

As the robot is pretending to write for the purpose of the interaction and is 
therefore not able to improve on its physical skills itself, 
This work represents the first teachable robotic agent which is 
being taught a physical skill for the benefit of the human teacher, through the
learning by teaching paradigm.
